---
title: "Lab1"
output: html_document
date: "2022-07-22"
---

## Exercise 1: Basic Data Types in R

 Name : PRIYANSHU VYAS

 REG NO. : 20BCE1685
 
---

Convert TRUE to an integer

```{r}
a <- TRUE
as.integer(a)
```

---

Assign a string to a variable and extract any substring.

```{r}
v <- "HELLO WORLD!!"
substr(v,4,7)
```

---

Assign an integer value to two variables p & q

```{r}
p <- 4
q <- 7
```

---

Use R as a calculator to do basic arithmetic operations on p &q and store each result in different variables.

```{r}
A <- p+q
S <- p-q
M <- p*q
D <- p/q
A;S;M;D
```

---

Calculate sqrt(p) and perform log2 transformation on the result.

```{r}
sp <- sqrt(p)
log2(sp)
```

---

Calculate the 10-based logarithm of 100 and multiply the result with cosine of π.

```{r}
log10(100)*cos(pi)
```

---

Create a vector ‘x’ using : operator from -2 to 2.

```{r}
x <- -2:2
x
```

---

Create a vector ‘y’ using c() with values 1 to 10. What is the dimension of y and length of y.

```{r}
y <- c(1:10)
y;dim(y);length(y)
```

---

Create two vectors small and caps with first 5 alphabets in lower case and last 5 alphabets in upper case respectively. Bind it row and column wise.

```{r}
small <- c('a','b','c','d','e')
caps <- c('V','W','X','Y','Z')
rbind(small,caps);cbind(small,caps)
```

---

Create a matrix M=[[1,4,3],[-2,8,6],[5,-1,7]]  and find  MxMxM.

```{r}
M <- matrix(data = c(1,4,3,-2,8,6,5,-1,7),3,3,T)
M;M%*%M%*%M
```

---

Find the result of element wise multiplication of M by M.

```{r}
M*M
```


---

Find the transpose, inverse and determinant of M.

```{r}
t(M);solve(M);det(M)
```

---