---
title: "Lab2"
output: html_document
date: "2022-07-29"
---

Reg. No: 20BCE1685

Name: PRIYANSHU VYAS


### Part 1: Creating a Data Frame

---

Create a data frame by considering 5 students and 4 events. Each event has a maximum score of 10. If a student participates in an event, its entry contains the value and 0 otherwise.

```{r}
Event <- data.frame(stname=c("Aditya","Pratik","Kishore","Aniket","Himanshu"),event1=c(0,10,1,3,4),event2=c(0,10,1,3,4),event3=c(0,10,1,3,4),event4=c(0,10,1,3,4))
```

---

View the contents of the data frame.

```{r}
Event
```

---

Find the Total score of each participant.

```{r}
rs <- rowSums(Event[2:5])
rs
```

---

Append a column to include the total score of the participants and the view the data frame.

```{r}
Event$Total <- rs
Event
```

---

Find the maximum score and display the name of the participant who scored 

```{r}
Event$stname[which.max(Event$Total)]
```

---

Find the avg of the events and append as a new row in the data frame.

```{r}
Event <- rbind(Event,
c("Avg",mean(Event$event1),
mean(Event$event2),
mean(Event$event3),
mean(Event$event4),
mean(Event$Total))
)
```

---

### Part 2: Indexing and Slicing data frames

---

Read the content of ‘Events.csv’ in a data frame and view it.

```{r}
write.csv(Event,"Event.csv")
read.csv("Event.csv")
```

---

Access the scores of participants in event2 using the column name.

```{r}
Event$event2
```

---

Use index number to retrieve the same data.

```{r}
Event[3]
```

---

Extract the score of third participant in event3.

```{r}
Event$event3[3]
```

---

Extract the scores of the first and second participant in all the events.

```{r}
Event[1:2,]
```

---

Display the names and total scores of all participants.

```{r}
Event
```

---

Make the column “name” as the row index of the data frame.

```{r}
row.names(Event) <- colnames(Event)
Event
```

---

Display the names of the students participated in event3.

```{r}
i<-0
for (score in Event$event3) {
  i<-i+1
  if(score!=0)
  {
     print(Event$stname[i]) 
  }
  if(i==5)break
}
```

---

Obtain the names whose total score is above its average.

```{r}
totalScore <- Event$Total
i <- 0
avg <- Event$Total[6]
for(score in totalScore)
{
  i<-i+1
    if(score>avg)
    {
      print(Event$stname[i])
    }
    
  if(i==5)break
}
```

---