---
title: "Lab2_29-07-22"
output: html_document
---
### Reg. No: 20BCE1685
### Name: PRIYANSHU VYAS
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

Create a data frame by considering 5 students and 4 events. Each event has a maximum score of 10. If a student participates in an event, its entry contains the value and 0 otherwise.

***
```{r}

Event <- data.frame(stname=c("Aditya","Pratik","Kishore","Aniket","Himanshu"),event1=c(0,10,1,3,4),event2=c(0,10,1,3,4),event3=c(0,10,1,3,4),event4=c(0,10,1,3,4))

```
***

View the contents of the data frame.

***
```{r}
Event
```
***

Find the Total score of each participant.

***
```{r}
rs <- rowSums(Event[2:5])
rs
```
***

Append a column to include the total score of the participants and the view the data frame.

***
```{r}
Event$Total <- rs
Event
```
***

Find the maximum score and display the name of the participant who scored 

***
```{r}
Event$stname[which.max(Event$Total)]
```
***

Find the avg of the events and append as a new row in the data frame.

***
```{r}
rbind(Event,
c("Avg",mean(Event$event1),
mean(Event$event2),
mean(Event$event3),
mean(Event$event4),
mean(Event$Total))
)
```

