---
title: "Lab3"
author: "PRIYANSHU VYAS 20BCE1685"
date: "05/08/2022"
output: html_document
---
***
    1. Install the package MASS.
***
```{r}
install.packages("MASS")
```
***
    2. Import the package MASS.
***
```{r}
library(MASS)
data("survey")
```
***
    3. Display the structure of the data survey.
***
```{r}
str(survey)
```
***
    4. Check the class and type of the data set survey in MASS.
***
```{r}
class(survey)
typeof(survey)
```
***
    5. Get the number of rows and columns of the survey data frame.
***
```{r}
nrow(survey);ncol(survey)
```
***
    6. Get the dimension of the survey data frame.
***
```{r}
dim(survey)
```
***
    7. Provide the statistical summary of the data frame.
***
```{r}
summary(survey)
```
***
    8. Display the column names of the survey data frame
***
```{r}
colnames(survey)
```
***
    9. Retrieve the top 3 rows from the data frame.
***
```{r}
head(survey,3)
```
***
    10. Extract the bottom 2 rows from the data frame.
***
```{r}
tail(survey,2)
```
***
    11. Filter all male left handers.	
***
```{r}
Male_LH <- subset(survey,Sex=="Male" &W.Hnd=="Left")
Male_LH
```
***
    12. Display all female right handers who keep right on top while clapping.
***
```{r}
Female_RH <- subset(survey,Sex=="Female" &W.Hnd=="Right" &Clap=="Right")
Female_RH
```
***
    13. Display all students who never exercise.
***
```{r}
No_Exer <- subset(survey,Exer=="None")
No_Exer
```
***
    14. Display only the gender, age and writing hand of the students.
***
```{r}
subset(survey,select = c(Sex,Age,W.Hnd))
```
***
    15. Display the age, pulse rate and writing hand span of female left handers.
***
```{r}
subset(survey,Sex=="Female" &W.Hnd=="Left",select = c(Age,Pulse,W.Hnd))
```
***
    16. Introduce a new column hand_span which contains the value as difference between the span of writing hand and non-writing hand and display it along with gender, writing hand and non-writing hand span.
***
```{r}
survey$hand_span <- survey$Wr.Hnd-survey$NW.Hnd
subset(survey,select = c(hand_span,Sex,Wr.Hnd,NW.Hnd))
```
***
    17. Display the average writing span of male and female left handers.
***
```{r}
Avgm <- subset(survey,Sex=="Male" &W.Hnd=="Left",select = Wr.Hnd)
mean(Avgm$Wr.Hnd)
Avgm <- subset(survey,Sex=="Female" &W.Hnd=="Left",select = Wr.Hnd)
mean(Avgm$Wr.Hnd)
```
***
    18. Find the maximum pulse rate of male left and right handers.
***
```{r}
MAX <- subset(survey,Sex=="Male",select = Pulse)
MAX <- na.omit(MAX)
max(MAX)
```

---