---
title: "Assessment 1"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---
### Reg. No: 20BCE1685

### Name: Priyanshu Vyas

### Frame any 10 questions for data manipulation


```{r}
library(MASS)
data(biopsy)
```


* * *

    1. Display the str and summary of the dataset.

* * *

```{r}
str(biopsy);
summary(biopsy);
```

* * *

    2. Display first six and last six entries of the given dataset.

* * *

```{r}
head(biopsy);
tail(biopsy);
```



* * *

    3. Write and read(in a variable) the dataset in csv format(in project directory).

* * *

```{r}
setwd("/home/student/20BCE1685");
write.csv(biopsy,'dataset.csv');
df <- read.csv('dataset.csv');
```



* * *

    4. Check for the NA values in dataset and print the rows containing NA values and omit them.

* * *

```{r}
sum(is.na(biopsy));
biopsy[!complete.cases(biopsy),];
biopsy <- na.omit(biopsy);
sum(is.na(biopsy));
```



* * *

    5. Display all the unique classes from the dataset and print no of patients in each class.

* * *

```{r}
library(dplyr)
unique(biopsy$class);
biopsy %>%
  group_by(class) %>%
  summarise(count = n())
```



* * *

    6. Display all the rows which are having V1 greater than five and class equal to benign.

* * *

```{r}
subset(biopsy,V1>5&class=='benign');
```



* * *

    7. Calculate the sum of all the nine attributes(V1..V9) given and add it in the dataframe.

* * *

```{r}
biopsy$Attr <- rowSums(biopsy[2:10])
head(biopsy)
```



* * *

    8. Display all the ID's,class and Attr which has class equal to malignant and Atrr is greater than 35.

* * *

```{r}
head(subset(biopsy,class=='malignant'&Attr>35,select = c(ID,class,Attr)));
```



* * *

    9. Display all the duplicate IDs.

* * *

```{r}
counts <- biopsy %>%
    group_by(ID) %>%
    summarise(
      count = n()
      )
subset(counts,select=ID,count>1)
```



* * *

    10. Display the ID and mean of all nine attributes by grouping ID's.

* * *

```{r}
biopsy %>%
    group_by(ID) %>%
    summarise(
      select = rowMeans(biopsy[2:10])
      )
```
